\Large Inferential Analysis of the Supreme Court Citation Network

### 2018-04-26 Tex/paper.tex
results of new model

>>>>

  \begin{figure}[H]
\includegraphics[width=15cm]{justice_popularity}
\caption{Nodeifactor Majority Opinion Writer. Baseline= LDBrandeis }
 \label{number_supporting}
\vspace{-.25cm}
\end{figure}

 \begin{figure}[H]
\includegraphics[width=15cm]{justice_activity}
\caption{Nodeofactor Majority Opinion Writer. Baseline= LDBrandeis }
 \label{number_supporting}
\vspace{-.25cm}
\end{figure}

 \begin{figure}[H]
  \begin{tabular}{c}
\includegraphics[width = 1\textwidth, trim= 0.1cm 1cm 0.1cm .1cm,clip=true]{issuearea_activity}
 \\
\includegraphics[width = 1\textwidth, trim= 0.1cm 1cm 0.1cm .1cm,clip=true]{issuearea_popularity}
\end{tabular}
\caption{Issue Area Popularity and Activity (nodeifactor and nodeofactor). Baseline is Issue Area 'Criminal Procedure'.}
\end{figure}

 \begin{figure}[H]
\includegraphics[width=15cm]{heatplot_issue_area}
\caption{Nodemix Issue Area. Sender14Receiver14 and Sender14Receiver13 couldnt be estimated.}
 \label{number_supporting}
\vspace{-.25cm}
\end{figure}
